Mo' Betta Gaia Distance Measurements, \\ Using Gaia + APASS photometry

### 2017-02-09 paperDistance/paper.tex
more content; rearrange order

The \gaia\ Mission will deliver more than a billion stellar distances.
Only a small fraction (but large number) of these distance
measurements will be purely astrometric:
\gaia\ uses astrometric parallax to determine the distances of the closer
stars, and calibrate spectrophotometric models.
These spectrophotometric models, in turn, along with \gaia's on-board
low-resolution $B_p\,R_p$ spectrophotometry, are used to provide
distance estimates to more distant stars.
The full stack required for these distance inferences is complex.
It involves modeling not just stars, but also the dust in the Milky Way,
and the response of the telescope itself.

With projects like \project{The Cannon} (DWH CITE) and \project{Avast}
(DWH CITE), we are exploring the extent to which our predictive models of
stars could be purely data-driven or statistical.
That is, under what circumstances could the data themselves deliver
more precise or more accurate models than any theoretical or
physics-based model?

@@

\section{Data}

\section{Methods}

@@

\subsection{Formalism} \label{bozomath}

\section{Results}

>>>>

The \gaia\ Mission (DWH CITE) will deliver more than a billion stellar distances.
Only a small fraction (but large number) of these distance
measurements will be purely astrometric:
\gaia\ uses astrometric parallax to determine the distances of the closer
stars, and calibrate spectrophotometric models.
These spectrophotometric models, in turn, along with \gaia's on-board
low-resolution $B_p\,R_p$ spectrophotometry, are used to provide
distance estimates to more distant stars (DWH CITE).
The full stack required for these distance inferences is complex.
It involves modeling not just stars, but also the dust in the Milky Way,
and the response of the telescope itself (DWH CITE).

With projects like \project{The Cannon} (DWH CITE) and \project{Avast}
(DWH CITE), we are exploring the extent to which our predictive models of
stars could be purely data-driven or statistical.
That is, under what circumstances could the data themselves deliver
more precise or more accurate models than any theoretical or
physics-based model?
The answer to this question is extremely context dependent: It depends
on what data are available, how much data are available, and what
questions are being answered.
In general, data-driven models contain fewer assumptions than
physics-driven models, but they are also usually less interpretable.
However, the \gaia\ use case is ideal for thinking about purely statistical
models of stars:
The nearby stars are measured at very high signal-to-noise and can be
used to anchor empirical models that can be applied to the more
distant stars.

Here we deliver a demonstration-of-concept project that shows that a
data-driven model of the \gaia\ data could in principle deliver very
precise distances, without any input of the physics of stellar
evolution, interiors, or photospheres...[DWH CONTENT]

@@

\section{Assumptions and methods}

@@

\section{Data and results}
